\LaTeXe\ guide for the Journal of Functional Programming

### 2019-05-02 papers/jfp/8-engineering.tex
Switch to MonadRandom

One tempting way of modelling non-determinism is to enrich \hs{Tasks} from
\hs{Applicative} or \hs{Monad} to \hs{Alternative} or \hs{MonadPlus},
respectively. Here is a task description corresponding to a spreadsheet with the
formula \cmd{B1 = A1 + RANDBETWEEN(1,2)}:

\begin{minted}[xleftmargin=10pt]{haskell}
sprsh3 :: Tasks MonadPlus String Integer
sprsh3 "B1" = Just $ Task $ \fetch -> (+) <$> fetch "A1"
                                          <*> (pure 1 <|> pure 2)
sprsh3 _    = Nothing
\end{minted}
\vspace{1mm}

>>>>

One way of modelling non-determinism is to \emph{demand that}~\hs{f}~\emph{has a
built-in source of non-determinism}, for example, by enriching
\hs{Tasks}~\hs{Monad} to \hs{Tasks}~\hs{MonadRandom} that has access to an
additional method
\hs{getRandom}~\hs{::}~\hs{(Integer,}~\hs{Integer)}~\hs{->}~\hs{m}~\hs{Integer},
i.e. a source of random numbers in a specified range. Here is a task description
corresponding to a spreadsheet with the formula \cmd{B1 = A1 + RANDBETWEEN(1,2)}:

\begin{minted}[xleftmargin=10pt]{haskell}
sprsh3 :: Tasks MonadRandom String Integer
sprsh3 "B1" = Just $ Task $ \fetch -> do a1 <- fetch "A1"
                                         r  <- getRandom (1,2)
                                         return (a1 + r)
sprsh3 _    = Nothing
\end{minted}
\vspace{1mm}
